Reproducibility and plant pathology: where do we stand and a way forward

### 2021-06-15 analysis/paper/paper.Rmd
Fix table reference to scoring criteria

Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table @\ref(tab:scoring)).

>>>>

Four individuals were assigned to rate a randomised list of journal articles using scoring criteria devised for the purposes of this research (Table \@ref(tab:scoring)).
